The role of motor inhibition during covert speech production

### 2022-01-31 manuscript.tex
updating the bib file's name
Updates from Overleaf

% \usepackage{url,hyperref,lineno,microtype,subcaption}
\usepackage{url,hyperref,lineno,microtype}
\usepackage[onehalfspacing]{setspace}

@@

% It can be rephrased as follows: given the putative role of the motor system in providing the multisensory content of motor imagery, how is it possible for motor imagery not to lead to motor execution?

@@

% Regarding the level at which motor inhibition may be applied during covert speech, we hypothesise that inhibition may apply both globally and in an effector-specific manner. Supporting this hypothesis, \cite{rieger_inhibition_2017} and \cite{bart_inhibitory_2021} have shown, using an action mode (overt vs. covert) switching paradigm, that the motor imagery of hand movements is accompanied by both global and effector-specific inhibition \citep[these results were also replicated in][]{bart_expectations_2021, bart_decay_2021, scheil_motor_2018}.

Based on evidence from electrophysiological, neuroimaging, and clinical studies, \cite{guillot_imagining_2012} suggested three possible routes whereby motor commands can be inhibited during motor imagery. First, motor inhibition can be integrated within the representation of the action to be produced internally, so that only subthreshold motor commands may be involved during motor imagery \citep[see also][]{bach_why_2021, glover_executive_2020}. Second, cerebral regions such as the pre-supplementary motor area (pre-SMA) \citep{kasess_suppressive_2008} or the right inferior frontal gyrus (rIFG) may weaken the motor commands that are emitted during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}. More precisely, the pre-SMA and the rIFG may work together to intercept the action process via the basal ganglia (subthalamic nucleus, STN), hence suppressing the output from the basal ganglia which in turn might inhibit the primary motor cortex \citep{aron_reactive_2011} (cf. Figure \ref{triangle}). In addition to such inter-regional inhibitory influences, motor imagery has been shown to be associated with modulations of short-interval intracortical inhibition within the primary motor cortex itself \citep{neige_unravelling_2020}.
Third, downstream regions in the cerebellum \citep[e.g.,][]{lotze_activation_1999}, in the brainstem \citep[e.g.,][]{jeannerod_neural_2001, jeannerod_motor_2006}, or at the spinal level may contribute to motor inhibition at a later stage.

Whether speech motor commands are emitted and subsequently inhibited during covert production is an issue that has been debated \citep[e.g.,][]{geva_inner_2018}. It has been suggested that during covert speech production, motor commands would be "simply specified in subthreshold way, requiring no active inhibition" \citep{geva_inner_2018}. Alternatively, motor commands may be emitted but subsequently inhibited by frontal or prefrontal regions such as the pre-SMA or rIFG \citep[e.g.,][]{jeannerod_neural_2001, loevenbruck_cognitive_2018, grandchamp_condialint_2019}. However, stating that covert speech (or motor imagery, more generally) only involves subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned or monitored" \citep[see also][]{scheil_motor_2018}. In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level. In this section, we provided empirical arguments in favour of the "active inhibition hypothesis". Proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during covert speech production, thus preventing execution.

@@

Here, we hypothesise that the progressive internalisation of speech during childhood may be related to the development of inhibitory abilities. This hypothesis could be tested in several ways. First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years). We would expect the ability to imagine actions, and speech specifically, to be positively correlated with motor inhibition at this age. \cite{wang_relationship_2021} provided correlational evidence that motor imagery (assessed in a hand laterality judgement task) and motor inhibition performance (assessed in a stop-signal task) improve together between 7 and 11 years old, and that these two abilities correlate at 7 years old but did not correlate at 11 years old. This suggests that inhibitory control may play a more prominent role role when speech is being internalised, but its role may weaken with expertise. This would be consistent with results from training studies suggesting that, with growing expertise, mental imagery increasingly relies on memory-based processes  \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.

@@

% \section*{Acknowledgements}

% None.

% \section*{Supplemental Data}

% \href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} should be uploaded separately on submission, if there are Supplementary Figures, please include the caption in the same file as the figure. LaTeX Supplementary Material templates can be found in the Frontiers LaTeX folder.

@@

\bibliographystyle{template/frontiersinSCNS_ENG_HUMS}
\bibliography{bibliography/covert_verbal_actions2}

\section*{Figure captions}

@@

% \begin{figure}[ht] % float was h! initially
% \begin{center}
% \includegraphics[width=0.75\textwidth]{figures/simulation_association.png} % This is a *.eps file
% \end{center}
% \caption{High-level depiction of the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms. The balance (weighting) between these two mechanisms during covert verbal actions depends on both task demands and "computational cost" (cf. text for more details), which are jointly determined by internal (individual) and external (situational) characteristics (e.g., expertise or (equivalently) task difficulty, noise, feedback perturbation).}\label{fig:1}
% \end{figure}

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/inhibitory_triangle.png} % This is a *.eps file
\end{center}
\caption{Plausible implementation of the cortical and subcortical inhibitory mechanisms responsible for the "proactive" (but implicit) response inhibition at play during covert speech production. The pre-SMA, posterior IFC, and STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production. Figure created with BioRender.com.}\label{triangle}
\end{figure}

>>>>

\usepackage{url,hyperref,lineno,microtype}
\usepackage[onehalfspacing]{setspace}

@@

@@

Based on evidence from electrophysiological, neuroimaging, and clinical studies, \cite{guillot_imagining_2012} suggested several possible routes whereby motor commands can be inhibited during motor imagery. First, cerebral regions such as the pre-supplementary motor area (pre-SMA) \citep{kasess_suppressive_2008} or the right inferior frontal gyrus (rIFG) may weaken the motor commands that are emitted during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}. More precisely, the pre-SMA and the rIFG may work together to intercept the action process via the basal ganglia (subthalamic nucleus), hence suppressing the output from the basal ganglia which in turn might inhibit the primary motor cortex \citep{aron_reactive_2011}. Second, motor imagery has been shown to be associated with modulations of short-interval intracortical inhibition within the primary motor cortex itself \citep{neige_unravelling_2020}. Third, downstream regions in the cerebellum \citep[e.g.,][]{lotze_activation_1999}, in the brainstem \citep[e.g.,][]{jeannerod_neural_2001, jeannerod_motor_2006}, or at the spinal level may contribute to motor inhibition at a later stage.

In addition to these three possible routes, another possibility highlighted by \cite{guillot_imagining_2012} is that motor inhibition can be integrated within the representation of the action to be produced internally, so that only subthreshold motor commands may be involved during motor imagery \citep[hereafter referred to as the "subliminal level hypothesis", see also][]{bach_why_2021, glover_executive_2020}. It has been suggested that during covert speech production, motor commands would be "simply specified in subthreshold way, requiring no active inhibition" \citep{geva_inner_2018}. However, stating that covert speech (or motor imagery, more generally) only involves subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned or monitored" \citep[see also][]{scheil_motor_2018}. In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level. In this section, we provided empirical arguments in favour of the "active inhibition hypothesis". Proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during covert speech production, thus preventing execution.

@@

Here, we hypothesise that the progressive internalisation of speech during childhood may be related to the development of inhibitory abilities. This hypothesis could be tested in several ways. First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years). We would expect the ability to imagine actions, and speech specifically, to be positively correlated with motor inhibition at this age. \cite{wang_relationship_2021} provided correlational evidence that motor imagery (assessed in a hand laterality judgement task) and motor inhibition performance (assessed in a stop-signal task) improve together between 7 and 11 years old, and that these two abilities correlate at 7 years old but did not correlate at 11 years old. This suggests that inhibitory control may play a more prominent role when speech is being internalised, but its role may weaken with expertise. This would be consistent with results from training studies suggesting that, with growing expertise, mental imagery increasingly relies on memory-based processes  \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.

@@

@@

\bibliographystyle{template/frontiersinSCNS_ENG_HUMS}
\bibliography{bibliography/covert_verbal_actions}

% \section*{Figure captions}

@@
